---
title: "usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
set.seed(400)
library(saferds)
```

## Define the Problem 
We aim to estimate the changes in ridership from a college safe ride progam from the first 8 weeks of Fiscal Year 2014 to Fiscal Year 2019 to the first 8 weeks of Fiscal Year 20. We will use the data set `all_data_sim` and the function `post_est`. 

## Define the Model

\[\begin{align*}
    Y & \sim \text{Poisson}(\mu_0 e^{-X\beta}) \\
    \beta & \sim \mathcal{N}(\mu, \tau^2\boldsymbol{\Sigma}) \\
    \mu_0 & = \log\left(\frac{1}{n}\sum_{i=1}^n Y_i\right)
\end{align*}\]


Where, 

* $\mu_0 = \frac{1}{n}\sum_1^n Y_i

* $\tau^2$ is a constant

* $\mu$ is a vector 

* When the data are independent, $\boldsymbol{\Sigma} = \boldsymbol{I}$

* When the data are dependent, $\boldsymbol{\Sigma} = (X^TX)^{-1}$


We first set up the design matrix and response variable from the data. We are interested in the effects of Week, Day, and the interaction between the two on the output of rides. We also want to include an indicator for the Fiscal Year 2020: 

```{r}
XMat <- model.matrix(~ all_data_sim$Week + all_data_sim$Day + I(all_data_sim$FY=="FY20") + all_data_sim$Week*all_data_sim$Day)

Y <- all_data_sim$Rides
```

## Define the Variables 

Next, we set our parameters according to our model. In this case we define: 

* $\tau^2 = 1$,

* $\mu = \boldsymbol{0}$,

* $\log(\mu_0)$ is defined as $\log{\mu_0}$, and 

* S=1000 where S is the number of samples we draw from the posterior distribution. 

For this model we will have no dependence. 


```{r}
tau2  <- 1
mu <- matrix(rep(0,ncol(XMat)))
logmu0 <-log(mean(Y))
S <- 1000
```


## Run the Estimator and Report Estimate

We can now run our estimator and calculate our log-liklihood estimates: 

```{r}
Est <- post_est(XMat, Y, mu, tau2, logmu0, S, depend=FALSE)
```

Because we are interested in the change in FY20 from the previous years, we want to know the likilhood, not the log-liklihood. We expoenetiate the calulated log likihood and find the appropriate confidence intervals. Note column 11 in our design matrix is the indicator for Fiscal Year 2020: This is the variable we are interested in. 

 
```{r}
colnames(XMat)[11]

Likeli_Est <- mean(exp(Est[[3]][,11]))
CI_Est <- quantile(exp(Est[[3]][,11]),c(0.025,0.975))

Likeli_Est
CI_Est
```
We estimate that our likelihood is 1.33 with a 95% confidence interval of (1.14, 1.53) We conclude that it is plausible that there was an increase in ridership in Fiscal Year 2020.  





