---
title: "usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(saferds)
```

## Define the Problem 
We aim to estimate the changes in ridership from a college safe ride progam from the first 8 weeks of FY14-FY19 to the first 8 weeks of FY20. 

## Define the Model



\[
\begin{align*}
    Y & \sim \text{Poisson}(\mu_0 e^{-X\beta}) \\
    \beta & \sim \mathcal{N}(\mu, \tau^2\boldsymbol{\Sigma}) \\
    \boldsymbol{\Sigma} & = (X^TX)^{-1} \\
    \mu_0 & = \log\left(\frac{1}{n}\sum_{i=1}^n Y_i\right)
\end{align*}\]


Where, 

* $\tau^2$ is a constant

* $\mu$ is a vector 


We first set up the design matrix and response variable from the data: 

```{r}
XMat <- model.matrix(~ all_data_sim$Week + all_data_sim$Day + all_data_sim$Week*all_data_sim$Day)

Y <- all_data_sim$Rides
```

## Define the Variables 

Next, we set our parameters: 

* tau2 controls the dependence from where we draw our sample from in the sampler. Where $\Sigma$ is our covariance matrix, we multiply $\tau^2\Sigma$ to get our dependence structure. The parameter is more closely definied in the Outline of the Sampler

* mu controls the mean from wehere we draw our sample from in the sample. The paramenter is more closely defined in the Outline of the Sampler. 

* logmu0 is defined as $\log\left(\frac{1}{n}\sum_{i=1}^n Y_i\right)$. This is used to center our data. 

* S is the number of iterations we run our sampler 


```{r}
tau2  <- 1
mu=matrix(rep(0,ncol(XMat)))
logmu0 <-log(mean(Y))
S=1000
```

## Outline the Sampler 

1. Choose ellipse: $\textbf{v} \sim N(\mu, \tau^2 \Sigma)$
2. Calculate the log likelihood threshold where L is the log likelihood function
  + $u \sim \text{Uniform}[0,1]$
  + $\log(y) = \log(L(\textbf{f})) + \log(u)$ 
3. Calculate and initial $\theta$ and interval
  + $\theta \sim \text{Uniform}[$[\theta_{min}, \theta_{max} ] \leftarrow [\theta -2\pi, \theta]$
4. $\textbf{f'} \leftarrow \textbf{f}\cos\theta + \textbf{v}\sin\theta$
5. if $\log(\textbf{f'}) > \log(y)$ then: 
  + Accept and return \textbf{f'}
  + else: Shrink bracket and try new point:
    + if $\theta <0$ then: $\theta_{min} \leftarrow \theta$, 
    + else: $\theta_{max} \leftarrow \theta$
    + $\theta \sim \text{Uniform}[\theta_{min}, \theta_{max}]$
    + Repeat from step 4 S times 


## Describe the input of the function 



## Describe the ouput of the function 




